---
output:
  md_document:
    variant: markdown_github
---

[![Travis-CI Build Status](https://travis-ci.org/noamross/texttable.svg?branch=master)](https://travis-ci.org/noamross/texttable)
[![Coverage Status](https://img.shields.io/codecov/c/github/noamross/texttable/master.svg)](https://codecov.io/github/noamross/texttable?branch=master)

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# texttable

This package imports tabular data that is stored in a variety of text formats.

## Install

    devtools::install_github('noamross/texttable')

## Usage


Enter tabular in the text format of your choice:

```{r}
library(texttable)
sample_table = "
                | My | Tabular  | Data |
                |----|----------|------|
                |   1| Sample 1 | 0.3  |
                |   2| Sample 2 | 1.2  |
               "
imported = texttable(sample_table)
imported
```

Note that `texttable()` will trim leading whitespace from string inputs by default.

Get tables out of text files, and even MS Word files:

```{r}
tables = texttable('tests/testthat/tables.markdown')
tables[[1]]
word_tables = texttable('tests/testthat/tables.docx')
word_tables[[1]]
```

## Known issues

Pandoc conversion of tables from `asciidoc`, `context`, `docbook`, `latex`,
`man`, `mediawiki`, `rtf`, `texinfo`, and `odt` formats has known issues and
does not always work. For these formats `texttable` will provide a warning,
as the output quality is unknown and will change with your current version of
Pandoc.
